NFL Draft Analysis: The Quarterback

### 2020-05-08 Drafting/qb_draft_analysis.Rmd
Scrape Offensive ROTY data and disable warnings on knit

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
setwd("/Users/PhilipIpe/Documents/Data Science/Projects/NFL Analytics/Drafting")
```

@@

  master_df <- rbind(master_df, df)
}
```
# Part 2: Data Processing and Preparation

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
library(tidyverse)
library(rvest)
setwd("/Users/PhilipIpe/Documents/Data Science/Projects/NFL Analytics/Drafting")
```

@@

  master_df <- rbind(master_df, df)
}
```

Next we will scrape the AP Offensive Rookie of the Year Winners from the same website.

```{r scrape_ROTY}

roty_url <- "https://www.pro-football-reference.com/awards/ap-offensive-rookie-of-the-year-award.htm"
draft_html <- read_html(roty_url)

roty_df <- draft_html %>%
  html_node("table") %>%
  html_table()
```
# Part 2: Data Processing and Preparation
